### 2021-08-12 documentos/notas/notas_carlos.tex
Don't tell me you're too blind to see

As a historical fact, the Krauss operators corresponding to one single qubit PCEs
are 
\begin{equation}
\{\openone/\sqrt2, \sigma_i/\sqrt2\}
\label{}
\end{equation}
(corresponding to the operation that leaves the component $\sigma_i$ invariant), 
see Eq. 8.95 of Chuang's book.  Visual inspection of the Krauss operators 
of two qubit PCEG (PCE generators) lead to the ansatz that 
the appropriate Krauss operators are 
\begin{equation}
\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma^{(k)}_{i_k}\right)/\sqrt2\right\}. 
\label{}
\end{equation}

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
\begin{equation}
\sigma_i \sigma_j \sigma_i =a^i_{j} \sigma_j,
\label{}
\end{equation}
with $a$ the matrix that appears in 
\eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
\eref{} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},

Counting, mostrar qe el numero de bichos que aparecen ahi coincide con el numero de generadores.

Show that they are unique

>>>>

As a historical fact, the Krauss operators corresponding to one single qubit PCEs
are 
\begin{equation}
\{\openone/\sqrt2, \sigma_i/\sqrt2\}
\label{eq:kraus:PCE}
\end{equation}
(corresponding to the operation that leaves the component $\sigma_i$ invariant), 
see Eq. 8.95 of Chuang's book.  Visual inspection of the Krauss operators 
of two qubit PCEG (PCE generators) lead to the ansatz that 
the appropriate Krauss operators are 
\begin{equation}
\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
\label{}
\end{equation}

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
\begin{equation}
\sigma_i \sigma_j \sigma_i =a^i_{j} \sigma_j,
\label{}
\end{equation}
with $a$ the matrix that appears in 
\eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
\eref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},
\begin{align}
\mcM[\rho] &= 
\frac{\openone}{\sqrt{2}} \rho\frac{\openone}{\sqrt{2}} 
 + 
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
&=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
&=\frac12 \rho
+ \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
&=
\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
\end{align}
However, $(1+\prod_k a^{i_k}_{j_k})/2$ is 0 or 1, proving the channel is a PCE.

We still have to show that except for $i_1=\cdots=i_n=0$, half of the numbers 
$(1+\prod_k a^{i_k}_{j_k})/2=1$, or equivalently, half of $\prod_k a^{i_k}_{j_k}=1$. 
Consider a particular $l$ such that $i_l \ne 0$. This will make half of 
the $\prod_k a^{i_k}_{j_k}$ 1 and half $-1$ (for fixed $l$). This also implies 
that half of the correlations of the density matrix are erased and half preserved 
so the channel is a PCEG.

Notice also that different choices of sets $\{i_k \}$ lead to different channels. This
can be seen noticing that if two channels were the same, this would imply that
the matrix representation of the corresponding superoperator of 
$\bigotimes_k \sigma_{i_k} \cdot \bigotimes_k \sigma_{i_k} $ would have to be
the same which is clearly false.

Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
generator. This notation is based on the action on each individual qubit. (ii) Counting the
number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
from other arguments.
